The Bug Catalog of the Maven Ecosystem

### 2014-01-20 docs/msr.tex
minor changes, fixes

In this paper we present: a) the experiment performed to obtain the
collection of the metric results that the FindBugs tool produces and
b) how researchers can use the dataset and include it in their research.

@@

With the {\sc jar} list at hand, we created a series of processing tasks
and added them to task queue mechanism (a Rabbit{\sc mq} message
broker). Then we executed twenty five (Unix-based)
workers (custom Python scripts) that checked out tasks
from the queue, processed the data and stored the
results to the data repository (a Mongo{\sc db}).

>>>>

In this paper we present: a) the experiment performed to obtain the
collection of the metric results that the FindBugs tool produces 
for every project version of the repository (115,214 {\sc jar}s)
and b) how researchers can use the dataset and include it in their research.

@@

With the {\sc jar} list at hand, we created a series of processing tasks
and added them to a task queue mechanism (a Rabbit{\sc mq} message
broker). Then we executed twenty five workers (custom Python scripts)
that checked out tasks from the queue, processed each project version
and stored the results to the data
repository (a Mongo{\sc db} database system).
